Looking for a Signal in the Noise: Revisiting Obesity and the Bacterial Microbiome

### 2016-02-25 Sze_ObesityMicrobiomeMeta_PeerJ_2016.Rmd
update table based on Amish data

Study <- c("Baxter", "Ross", "Goodrich", "Escobar", "Zupancic*", "HMP", "Wu", "Arumugam", "Turnbaugh**")

Age <- c("54.3 +/- 9.9", "57.0 +/- 11.2", "61.5 +/- 8.9", "38.1 +/- 11.1", "48.2 +/- 13.2", "26.1 +/- 5.0", "26.4 +/- 9.4", "56.5 +/- 7.7", "21 - 32")

Sex <- c("111|61", "48|15", "505|2", "14|16", "198|112", "127|129", "31|27", "45|40", "Not Available")

@@

BMI <- c("27.0 +/- 5.3", "31.6 +/- 5.3", "26.3 +/- 4.9", "27.4 +/- 4.5", "29.2 +/- 5.2", "24.1 +/- 3.4", "24.6 +/- 4.8", "27.8 +/- 5.8", "Not Available")

Min <- c(17.5, 22.1, 16.2, 19.5, 16.7, 19, 14.0, 18.6, "Not Available")

@@

*If numerical BMI information was not available then ranges and demographic information was taken from the authors published manuscript for this table.

**Only BMI group information was provided and only an age range was given.

>>>>

Study <- c("Baxter", "Ross", "Goodrich", "Escobar", "Zupancic", "HMP", "Wu", "Arumugam", "Turnbaugh*")

Age <- c("54.3 +/- 9.9", "57.0 +/- 11.2", "61.5 +/- 8.9", "38.1 +/- 11.1", "46.7 +/- 13.1", "26.1 +/- 5.0", "26.4 +/- 9.4", "56.5 +/- 7.7", "21 - 32")

Sex <- c("111|61", "48|15", "505|2", "14|16", "112|87", "127|129", "31|27", "45|40", "Not Available")

@@

BMI <- c("27.0 +/- 5.3", "31.6 +/- 5.3", "26.3 +/- 4.9", "27.4 +/- 4.5", "27.7 +/- 5.3", "24.1 +/- 3.4", "24.6 +/- 4.8", "27.8 +/- 5.8", "Not Available")

Min <- c(17.5, 22.1, 16.2, 19.5, 18.2, 19, 14.0, 18.6, "Not Available")

@@

*Only BMI group information was provided and only an age range was given.
